{{< var titll >}}

### 2024-07-12 presentation.qmd
break

:::
## {{< var sec2.un3 >}}

>>>>

## {{< var sec2.un3 >}}

:::: {.columns}

::: {.column width="50%"}

*Standard form*

Setting the first three parameters:

- $x_i=\frac{s_i}{s_i+t_i}$
- $y_i=\frac{u_i}{u_i+v_i}$
- $\zeta_i=\frac{u_i+v_i}{s_i+t_i}$

Backsolve for

- $\alpha_i(x_,y_i,\zeta_i)=\frac{x_i+\zeta_i\cdot y_i}{\zeta_i+1}$
- $\lambda_i(x_i,y_i,\zeta_i)=\frac{x_i\zeta_i\cdot(1-y_i)}{\zeta_i+1}$

::: {.column width="50%"}

*Opposition form*

Setting the first three parameters:

- $g_i=\frac{s_i}{s_i+t_i}$
- $h_i=\frac{u_i}{u_i+v_i}$
- $\Gamma_i=\frac{u_i+d_i}{u_i+v_i}$

Backsolve for

- $\alpha_i(g_i,h_i,\Gamma_i)=\frac{x_i+\zeta_i\cdot y_i}{\zeta_i+1}$
- $\Omega_i(g_i,h_i,\Gamma_i)=\frac{x_i\zeta_i\cdot(1-y_i)}{\zeta_i+1}$

::::

**Properties**:

- 1<sup>st</sup> The total election outcome will be determined by *three* parameters: ( $x_i, y_i,\zeta_i$ ) under standard form and ( $g_i, h_i, \Gamma_i$ ) using hybrid form. 
- 2<sup>nd</sup> Changes in $\Gamma_i$ and $\zeta_i$ would in general have an impact on $\alpha_i$.

[Application 2: Rigged election process simulator]({{< var shn2 >}})

## {{< var sec2.un4 >}}

**Setting the prefered election outcome**

:::: {.columns}

::: {.column width="50%"}
Non-rigged election using standard form
```{r}
#app_n_out[[4]] 
```

::: {.column width="50%"}

Rigged election using standard form
```{r}
#app_ex1_out[[4]] 
```

::::

**Normal**
<br>
\begin{equation*}
f(x)_{0}^{1}=`r #paste0(round(polynom::polynomial(unname(pri_int_ex1)),3))`$
\end{equation*}

Election outome 
```{r, echo=F}
#pri_int_ex1
#polynom::integral(round(polynom::polynomial(unname(pri_int_ex1))),c(0,1))
#mean(app_ex1_cou$rdfc$alpha)
```

<br>
**Rigged**
<br>

$f(x)_{0}^{1}=`r #paste0(round(polynom::polynomial(unname(pos_int_ex1)),3))`$

Election outome
```{r, echo=F}
#polynom::integral(round(polynom::polynomial(unname(pos_int_ex1))),c(0,1))
#pos_int_ex1
```

### Rigged election example 1: applying normal form

- Setting for eaching precinct the first three parameters
 - $\alpha_i=<...>$ (i.e., equal to the prefered election outcome)
 - $x_i=\frac{a_i}{a_i+b_i}$ (true observations)
 - $y_i=\overset{\text{Manifold equation}}{\overbrace{\overset{}{M(x_i,\alpha_i,\underset{\text{outside information}}{...})}}}+\epsilon_t \text{ where } \epsilon_t \sim N(0,\sigma^2)$
- Backsolve for
 - $\zeta_i(x_i,\alpha_i,y_i)=\frac{x_i-\alpha_i}{\alpha_i-y_i}$
 - $\lambda_i(x_i,\zeta_i,y_i)=\frac{x_i-\zeta_i (1-y_i)}{\zeta_i+1}$

**Properties**:

- 3<sup>rd</sup> $y_i$ can now be determined by *two* equations
  - a. Tautology (must hold)
  - b. Manifold equation + error term (white noise)
- 4<sup>th</sup>. Changes in $\zeta_i$ - and as a corrollary $\Omega_i$ - is now 
  - a. Solely caused by the error term $\epsilon_i$ and, if used, the non-linear part of the Manifold equation.
  - b. Has no longer any causal impact on $\alpha_i$

### Rigged election example 2: applying hybrid form

- Setting for eaching precinct the first three parameters
 - $\alpha_i=<...>$ (i.e., equal to the prefered election outcome)
 - $h_i=\frac{s_i}{s_i+v_i}$ (true observations)
 - $g_i=\overset{\text{Manifold equation}}{\overbrace{\overset{}{M(h_i,\alpha_i,\underset{\text{outside information}}{...})}}}+\epsilon_t \text{ where } \epsilon_t \sim N(0,\sigma^2)$
- Backsolve form
 - $\Gamma_i(g_i,\alpha_i,h_i)=\frac{g_i-\alpha_i}{\alpha_i-h_i}$
 - $\Omega_i(g_i,\Gamma,h_i)=-\alpha_i+\frac{\Gamma_i+2g_i}{\Gamma_i+1}$

**Properties**:

- 5<sup>th</sup> $y_i$ can now be determined by *two* equations
  - a. Tautology (must hold)
  - b. Manifold equation + error term (white noise)
- 6<sup>th</sup> Changes in $\Gamma_i$ - and as a corrollary $\lambda_i$ - is now 
  - a. Solely caused by the error term $\epsilon_i$ and, if used, the non-linear part of the Manifold equation.
  - b. Has no longer any causal impact on $\alpha_i$

### Rigged election example 3: applying opposition form

- Setting for eaching precinct the first three parameters
 - $\lambda_i=<...>$ (i.e., equal or less than the prefered election outcome)
 - $n_i=\frac{a_i}{a_i+c_i}$ (true observations)
 - $m_i=\overset{\text{Manifold equation}}{\overbrace{\overset{}{M(n_i,\lambda_i,\underset{\text{outside information}}{...})}}}+\epsilon_t \text{ where } \epsilon_{t_i} \sim N(0,\sigma^2)$
- Backsolve for
 - $\Omega_i(n_i,m_i,\lambda_i) = \frac{\lambda_i(n_i-m_i)-m_i(2n_i-1)}{1-(n_i+m_i)}$
 - $\xi_i(n_i,m_i,\Omega_i)=\frac{m_i-\Omega_i}{\Omega_i-n_i}$

**Properties**:

- 7<sup>th</sup> $m_i$ can now be determined by *two* equations
  - a. Tautology (must hold)
  - b. Manifold equation + error term (white noise)
- 8<sup>th</sup> Changes in $\xi_i$ is now 
  - a. Solely caused by the error term $\epsilon_i$ and, if used, the non-linear part of the Manifold equation.
  - b. Has no longer any causal impact on $\lambda_i$
